\documentclass[12pt]{article}
\topmargin0.0cm
\headheight0.0cm
\headsep0.0cm
\oddsidemargin0.0cm
\textheight23.0cm
\textwidth16.5cm
\footskip1.0cm
\setlength\parindent{0pt}

\begin{document}

\title{Assignment 3: Questions}
\author{Ryan Bomalaski and Venkatesh Sekar}

\maketitle

\section*{Question Overview}
Part of the requirements process is asking involved questions to root out exactly what different stakeholders want from a project.  In order to produce this information, it is a good idea to prepare some questions ahead of time.  Below are the questions we have thought of for getting information from the corresponding stakeholders.


\section*{Questions Sorted by Stakeholder}
\subsection*{User}
\begin{itemize}
  \item What features would you look for in a memory assistance application?
  \item What are your notable memory-related daily struggles?
  \item If an application/hardware could be created to help memory impairment but needed active user input, would you use it?
\end{itemize}

\subsection*{Doctor/Caregiver}
\begin{itemize}
  \item What are the potential emergencies that may arise for your patient?
  \item How would it be best to notify you of those emergencies?
  \item What do you envision as useful aspects of a hardware/software solution for memory assistance and improvement?
\end{itemize}

\subsection*{Investor}
\begin{itemize}
  \item How much are you willing to invest?
  \item How much are you expecting as a minimum return?
  \item How soon are you expecting that level of a return?
\end{itemize}

\subsection*{Regulators}
\begin{itemize}
  \item What type of statutory compliance issues are we looking at?
  \item Will our form of wireless device communication require any kind of licensing or spectrum issues?
\end{itemize} 

\subsection*{Taxi Company/Rideshare}
\begin{itemize}
  \item What method of being notified of a potential fare works best for you?
  \item Do your drivers have ways of being contacted directly?
  \item Are your drivers able to assist with memory impaired individuals?
\end{itemize}

\subsection*{Emergency Response Services}
\begin{itemize}
  \item What method of being notified of emergencies works best for you?
  \item When an incident occurs, what kind of information would be beneficial to emergency responders?
\end{itemize}

\subsection*{Software Developers}
\begin{itemize}
  \item What roadblocks do you envision with this type of software/hardware system?
  \item How long do you envision a project of this magnitude to take?
  \item How can the development work be best divided and between how many workers?
\end{itemize} 

\subsection*{Software Testers}
\begin{itemize}
  \item What testable requirements do you look for in a project of this size/type?
  \item What kind of testing would be done to ensure compliance?
  \item What kind of relationship do you envision having with the developers?
  \item How do you see your communication with developers occurring?
\end{itemize}

\subsection*{Designer}
\begin{itemize}
  \item What sort of roadblocks do you envision with designing this type of project?
  \item What would most help you create a traceable data-flow?
\end{itemize}

\subsection*{Project Manager}
\begin{itemize}
  \item What kind of cost do you think a project of the kind will entail?
  \item What kind of man-power will be required to complete the project?
  \item What is a projected timetable from beginning development to delivery?
\end{itemize}

\subsection*{Hardware Engineer}
\begin{itemize}
  \item What are the costs of hardware of this type?
  \item How long to design and create a working prototype?
  \item What sort of user-expectations would take this project into the realm of difficult/impossible to create?
\end{itemize}

\subsection*{Factory Workers/Producers}
\begin{itemize}
  \item Can the Cogbit be made at scale?
  \item What kind of production cost are we looking at?
\end{itemize}

\section*{Questions for Consultant}
\begin{itemize}
\item What kind of features would be sought after in a memory management and assistance system?
\item What kind of cost would we run into producing both hardware and software components and what scale are we looking at?
\item What kind of regulatory issues might we run into?  Do we need to worry about medical or consumer regulatory bodies?
\end{itemize}

\end{document}